---
title: "R Notebook"
output: html_notebook
---

# Setup initial
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(include = FALSE)
#set environmental variables
rm(list = ls())
options(scipen = 999)
set.seed(42)

#load required packages (if not installed, pacman will install them)
if (!require("pacman")) install.packages("pacman");
library(pacman)
pacman::p_load(tidyverse, lubridate, tidytext,
               tm, topicmodels, topicmodels, Rcpp, 
               udpipe, car, stats, sentimentr, lexicon, 
               textdata, tokenizers, zoo, patchwork, ggforce, scales,
               vader, parallel, furrr, ggrain)
```

############## Section 1: Loading and filtering data ############## 

```{r echo=FALSE}
data_combined<- read_csv("data_clean/data_combined_posts_comments_clean.csv", show_col_types = FALSE)
data_combined
```

# Platform Analysis (WideSpread)


```{r echo=FALSE}
library(tidyverse)
library(stringr)
library(lubridate)

# Load the dataset
data_combined <- read_csv("data_clean/data_combined_posts_comments_clean.csv", show_col_types = FALSE)

# Filter data by date ranges
date_range <- data_combined %>% filter(ymd_hms(date) >= ymd("2019-01-01") & ymd_hms(date) <= ymd("2021-12-31"))
pre_pandemic <- data_combined %>% filter(ymd_hms(date) >= ymd("2019-01-01") & ymd_hms(date) <= ymd("2020-03-31"))
during_pandemic <- data_combined %>% filter(ymd_hms(date) >= ymd("2020-04-01") & ymd_hms(date) <= ymd("2021-12-31"))


# Platforms
platform_unigrams <- c("technology", "device", "innovation", "smartphone", "online", "gadget", "handset", "network", "electronic", "machine", "apparatus", "tech", "platform", "phone", "machinery", "app", "cell", "mobile", "community", "digital", "application", "media", "service", "web", "browser", "operating system", "streaming", "e-commerce", "search engine", "virtual reality", "augmented reality", "cloud", "gaming", "podcasts","television", "tv", "notifications", "smartwatch")

platform_bigrams <- c("technology social", "technology", "social media", "digital media", "device", "media electronic", "innovation", "community tech", "gadget apparatus", "mobile phone", "media service", "phone handset", "online media", "social", "smartphone", "electronic media", "online", "gadget", "device platform", "online community", "smartphone technology", "streaming service", "virtual world", "e-commerce platform", "gaming console", "video conference", "operating system", "search engine", "web browser", "cloud service", "social network", "dating app", "video games", "smart watch")

# Extending the 'platform_unigrams' list with popular applications/social media platforms
social_platforms <- c("Facebook", "YouTube", "WhatsApp", "Messenger", "WeChat", "Instagram", "TikTok", "QQ", "Douyin", "Sina Weibo", "Qzone", "Snapchat", "Reddit", "Twitter", "LinkedIn", "Pinterest", "Telegram", "Viber", "Discord", "Twitch", "Baidu Tieba", "Signal", "Skype", "Zoom", "Microsoft Teams", "Slack", "Clubhouse", "Tumblr", "Spotify","Netflix", "Tinder", "Hinge", "DisneyPlus")


# Modified function to count occurrences of terms
count_terms <- function(data, terms, token_type = "words") {
  if (token_type == "bigrams") {
    tokenized_data <- data %>%
      unnest_tokens(output = word, input = body, token = "ngrams", n = 2)
  } else {
    tokenized_data <- data %>%
      unnest_tokens(output = word, input = body)
  }
  
  tokenized_data %>%
    count(word) %>%
    filter(word %in% terms) %>%
    arrange(-n)
}

# Count occurrences for pre-pandemic and during pandemic
pre_pandemic_platforms <- count_terms(pre_pandemic, platform_unigrams)
during_pandemic_platforms <- count_terms(during_pandemic, platform_unigrams)

pre_pandemic_platforms_bigram <- count_terms(pre_pandemic, platform_bigrams, "bigrams")
during_pandemic_platforms_bigram <- count_terms(during_pandemic, platform_bigrams, "bigrams")

# Display top 10 platforms for each period
head(pre_pandemic_platforms, 20)
head(during_pandemic_platforms, 20)

head(pre_pandemic_platforms_bigram, 20)
head(during_pandemic_platforms_bigram, 20)


```
## comparing pre vs post covid 

```{r echo=FALSE}
# Load necessary library
library(ggplot2)

# Join the two datasets to compare side-by-side
comparison_data <- full_join(pre_pandemic_platforms, during_pandemic_platforms, by = "word", suffix = c("_pre", "_during"))

# Fill NA values with 0
comparison_data[is.na(comparison_data)] <- 0

# Melt the data for ggplot
comparison_data_long <- comparison_data %>% 
  gather(key = "period", value = "count", n_pre, n_during)

# Create the plot
covid_platforms_uni <- ggplot(comparison_data_long, aes(x = reorder(word, count), y = count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Platform Mentions Pre and During Pandemic", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()


# bigrams

# Join the two datasets to compare side-by-side for bigrams
comparison_data_bigram <- full_join(pre_pandemic_platforms_bigram, during_pandemic_platforms_bigram, by = "word", suffix = c("_pre", "_during"))

# Fill NA values with 0 for bigrams
comparison_data_bigram[is.na(comparison_data_bigram)] <- 0

# Melt the data for ggplot for bigrams
comparison_data_bigram_long <- comparison_data_bigram %>% 
  gather(key = "period", value = "count", n_pre, n_during)

covid_platforms_uni
# Create the plot for bigrams
ggplot(comparison_data_bigram_long, aes(x = reorder(word, count), y = count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Platform Bigram Mentions Pre and During Pandemic", 
       x = "Platform Bigrams", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

#Without the term social media for bigrams

# List of social media terms to be removed from bigrams
social_media_terms <- c("Facebook", "YouTube", "WhatsApp", "Messenger", "WeChat", "Instagram", "TikTok", "QQ", "Douyin", "Sina Weibo", "Qzone", "Snapchat", "Reddit", "Twitter", "LinkedIn", "Pinterest", "Telegram", "Viber", "Discord", "Twitch", "Baidu Tieba", "Signal", "Skype", "Zoom", "Microsoft Teams", "Slack", "Clubhouse", "Tumblr", "Spotify")

# Filter out bigrams containing social media terms
comparison_data_bigram_filtered <- comparison_data_bigram %>% 
  filter(!str_detect(word, paste(social_media_terms, collapse = "|")))

# Melt the filtered data for ggplot
comparison_data_bigram_filtered_long <- comparison_data_bigram_filtered %>% 
  gather(key = "period", value = "count", n_pre, n_during)

#shrink to more relevant categories


```
As a percentage
```{r}
# Calculate total mentions for each period
total_pre_pandemic_platforms <- sum(comparison_data$n_pre)
total_during_pandemic_platforms <- sum(comparison_data$n_during)

# Calculate percentages for unigrams
comparison_data$percentage_pre <- (comparison_data$n_pre / total_pre_pandemic_platforms) * 100
comparison_data$percentage_during <- (comparison_data$n_during / total_during_pandemic_platforms) * 100

# Melt the data for ggplot
comparison_data_long_percentage <- comparison_data %>% 
  gather(key = "period", value = "percentage", percentage_pre, percentage_during)

# Create the plot for unigrams using percentages
covid_platforms_uni_percentage <- ggplot(comparison_data_long_percentage, aes(x = reorder(word, percentage), y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Platform Mentions Pre and During Pandemic (Percentage)", 
       x = "Platforms", y = "Percentage of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

# Calculate total mentions for bigrams for each period
total_pre_pandemic_platforms_bigram <- sum(comparison_data_bigram$n_pre)
total_during_pandemic_platforms_bigram <- sum(comparison_data_bigram$n_during)

# Calculate percentages for bigrams
comparison_data_bigram$percentage_pre <- (comparison_data_bigram$n_pre / total_pre_pandemic_platforms_bigram) * 100
comparison_data_bigram$percentage_during <- (comparison_data_bigram$n_during / total_during_pandemic_platforms_bigram) * 100

# Melt the data for ggplot for bigrams
comparison_data_bigram_long_percentage <- comparison_data_bigram %>% 
  gather(key = "period", value = "percentage", percentage_pre, percentage_during)

# Create the plot for bigrams using percentages
covid_platforms_bi_percentage <- ggplot(comparison_data_bigram_long_percentage, aes(x = reorder(word, percentage), y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Platform Bigram Mentions Pre and During Pandemic (Percentage)", 
       x = "Platform Bigrams", y = "Percentage of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

covid_platforms_uni_percentage
covid_platforms_bi_percentage

```

## Platform Totals

```{r echo=FALSE}
# Count occurrences for date_range
date_range_platforms <- count_terms(date_range, platform_unigrams)
date_range_platforms_bigram <- count_terms(date_range, platform_bigrams, "bigrams")


library(RColorBrewer)
# Create the plot for unigrams
platform_total <- ggplot(date_range_platforms, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[1]) +
  labs(title = "Platform Totals for Unigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()


# Create the plot for bigrams
platform_total_bi <- ggplot(date_range_platforms_bigram, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[2]) +
  labs(title = "Platform Totals for Bigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()

head(date_range_platforms,10)
head(date_range_platforms_bigram,10)

platform_total
platform_total_bi
```
as persentages
```{r}
# Calculate total number of platform mentions for the date range
total_platforms_date_range <- sum(date_range_platforms$n)

# Calculate percentages for unigrams
date_range_platforms$percentage <- (date_range_platforms$n / total_platforms_date_range) * 100

# Calculate total number of platform bigram mentions for the date range
total_platforms_date_range_bigram <- sum(date_range_platforms_bigram$n)

# Calculate percentages for bigrams
date_range_platforms_bigram$percentage <- (date_range_platforms_bigram$n / total_platforms_date_range_bigram) * 100

# Create the plot for unigrams with percentages
platform_total_percentage <- ggplot(date_range_platforms, aes(x = reorder(word, percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[1]) +
  labs(title = "Platform Totals for Unigrams (Percentage)", 
       x = "Platforms", y = "Percentage of Mentions") +
  theme_minimal() + coord_flip()

# Create the plot for bigrams with percentages
platform_total_bi_percentage <- ggplot(date_range_platforms_bigram, aes(x = reorder(word, percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[2]) +
  labs(title = "Platform Totals for Bigrams (Percentage)", 
       x = "Platforms", y = "Percentage of Mentions") +
  theme_minimal() + coord_flip()

# Display top platform mentions for each type
head(date_range_platforms,10)
head(date_range_platforms_bigram,10)

platform_total_percentage
platform_total_bi_percentage

```




# Social Media Platforms

```{r echo=FALSE}
# Create a function to count mentions in the pre-pandemic and during-pandemic periods
count_mentions <- function(data, term) {
  pre_pandemic_count <- sum(str_detect(tolower(data$body[data$date >= as.Date("2019-01-01") & data$date <= as.Date("2020-03-31")]), paste0("\\b", tolower(term), "\\b")))
  during_pandemic_count <- sum(str_detect(tolower(data$body[data$date >= as.Date("2020-04-01") & data$date <= as.Date("2021-12-31")]), paste0("\\b", tolower(term), "\\b")))
  return(data.frame(Term = term, Pre_Pandemic = pre_pandemic_count, During_Pandemic = during_pandemic_count))
}

# Get mentions for each platform
platform_mentions <- lapply(social_platforms, function(platform) {
  count_mentions(data_combined, platform)
})

# Bind the data frames in the list to a single data frame
platform_mentions_df <- do.call(rbind, platform_mentions)

# Add a column for total mentions and sort
platform_mentions_df$Total_Mentions <- platform_mentions_df$Pre_Pandemic + platform_mentions_df$During_Pandemic
platform_mentions_df <- platform_mentions_df[order(-platform_mentions_df$Total_Mentions), ]

# Plot the data using ggplot2
ggplot(platform_mentions_df, aes(x = reorder(Term, Total_Mentions))) +  # reordering based on Total_Mentions
  geom_bar(aes(y = Pre_Pandemic, fill = "Pre Pandemic"), stat = "identity", position = "dodge") +
  geom_bar(aes(y = During_Pandemic, fill = "During Pandemic"), stat = "identity", position = "dodge") +
  labs(title = "Mentions of Social Media Platforms Pre and During Pandemic", 
       x = "Platform", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2", name = "Period") + coord_flip()


```

```{r echo=FALSE}
# Required libraries
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(plotly)
library(lubridate)
library(stringr)
library(ggridges)

# Assuming you've already loaded data_combined and set social_media_terms
# Filter the data within the date range
date_range <- data_combined %>% 
  filter(ymd_hms(date) >= ymd("2019-01-01") & ymd_hms(date) <= ymd("2021-12-31"))

# Define the function to calculate monthly mentions for each platform
calculate_monthly_mentions <- function(platform, data) {
  mentions_df <- data %>%
    filter(str_detect(tolower(body), paste0("\\b", tolower(platform), "\\b"))) %>%
    count(Month = floor_date(date, "month")) %>%
    rename(mentions = n)
  
  mentions_df$Platform <- platform
  
  return(mentions_df)
}

# Apply function to each platform and combine results
all_platform_mentions <- do.call(rbind, lapply(social_media_terms, calculate_monthly_mentions, data = date_range))

# Identify top 10 platforms based on total mentions
top_platforms <- all_platform_mentions %>%
  group_by(Platform) %>%
  summarize(TotalMentions = sum(mentions), .groups = 'drop') %>%
  arrange(desc(TotalMentions)) %>%
  head(10) %>%
  pull(Platform)

# Filter data for only the top 10 platforms
filtered_mentions <- all_platform_mentions %>% filter(Platform %in% top_platforms)

# Plot the data
ggplot(filtered_mentions, aes(x = Month, y = mentions, color = Platform, group = Platform)) +
  geom_line(size = 1) +
  labs(title = "Monthly Mentions of Top 10 Platforms (2019-2021)", 
       x = "Month", y = "Mentions", color = "Platform") +
  theme_minimal() +
  scale_color_brewer(palette = "Dark2") +
  theme(legend.position = "top")

ggplot(filtered_mentions, aes(x = mentions, y = Platform, fill = Platform, group = Platform)) +
  geom_density_ridges(scale = 3) +
  labs(title = "Distribution of Monthly Mentions of Top 10 Platforms (2019-2021)", 
       x = "Mentions per Month", y = "Platform", fill = "Platform") +
  theme_minimal() +
  scale_fill_brewer(palette = "Paired") +
  theme(legend.position = "top")


```


# Strategies

```{r echo=FALSE}

# Define strategies
strategy_unigrams <- c("reducing", "switching", "break", "quitting", "leaving", "meditating", "unplugging", "limiting", "detoxing", "avoiding", "minimizing", "disconnecting", "resting", "sabbatical", "offlining", "restricting", "abstaining", "pausing", "refraining", "deactivating", "logging off", "ignoring", "muting", "filtering", "decluttering", "simplifying",  "rebooting", "recharging", "grounding", "backtracking", "outsourcing", "scheduling", "fading", "blocking", "committing", "retreating", "downshifting", "prioritizing", "tool")


strategy_bigrams <- c("approach way", 'cold turkey', "disconnection programs", "solution approach", "seeking support", "practice method", "way practice", "strategy solution", "best practices", "action plan", "contingency plan", "proven method", "game plan", "Easing off", "blue light")

# Count occurrences for pre-pandemic and during pandemic for strategy unigram.
pre_pandemic_strategies <- count_terms(pre_pandemic, strategy_unigrams)
during_pandemic_strategies <- count_terms(during_pandemic, strategy_unigrams)

# Count occurrences for pre-pandemic and during pandemic for strategy bigrams
pre_pandemic_strategies_bigram <- count_terms(pre_pandemic, strategy_bigrams, "bigrams")
during_pandemic_strategies_bigram <- count_terms(during_pandemic, strategy_bigrams, "bigrams")

# Display top strategy mentions for each period
head(pre_pandemic_strategies, 20)
head(during_pandemic_strategies, 20)
head(pre_pandemic_strategies_bigram, 20)
head(during_pandemic_strategies_bigram, 20)

# Comparing pre vs post covid for strategy unigrams
comparison_data_strategy <- full_join(pre_pandemic_strategies, during_pandemic_strategies, by = "word", suffix = c("_pre", "_during"))
comparison_data_strategy[is.na(comparison_data_strategy)] <- 0
comparison_data_strategy_long <- comparison_data_strategy %>% 
  gather(key = "period", value = "count", n_pre, n_during)

# Plot for strategy unigrams
ggplot(comparison_data_strategy_long, aes(x = reorder(word, count), y = count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Strategy Mentions Pre and During Pandemic", 
       x = "Strategies", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

# Comparing pre vs post covid for strategy bigrams
comparison_data_strategy_bigram <- full_join(pre_pandemic_strategies_bigram, during_pandemic_strategies_bigram, by = "word", suffix = c("_pre", "_during"))
comparison_data_strategy_bigram[is.na(comparison_data_strategy_bigram)] <- 0
comparison_data_strategy_bigram_long <- comparison_data_strategy_bigram %>% 
  gather(key = "period", value = "count", n_pre, n_during)

# Plot for strategy bigrams
ggplot(comparison_data_strategy_bigram_long, aes(x = reorder(word, count), y = count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Strategy Bigram Mentions Pre and During Pandemic", 
       x = "Strategy Bigrams", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

```
as persentages
```{r}
# Calculate total number of strategy mentions for each period
total_pre_pandemic <- sum(pre_pandemic_strategies$n)
total_during_pandemic <- sum(during_pandemic_strategies$n)

# Calculate percentages for pre-pandemic and during pandemic for strategy unigram
pre_pandemic_strategies$percentage <- (pre_pandemic_strategies$n / total_pre_pandemic) * 100
during_pandemic_strategies$percentage <- (during_pandemic_strategies$n / total_during_pandemic) * 100

# Calculate total number of strategy bigram mentions for each period
total_pre_pandemic_bigram <- sum(pre_pandemic_strategies_bigram$n)
total_during_pandemic_bigram <- sum(during_pandemic_strategies_bigram$n)

# Calculate percentages for pre-pandemic and during pandemic for strategy bigram
pre_pandemic_strategies_bigram$percentage <- (pre_pandemic_strategies_bigram$n / total_pre_pandemic_bigram) * 100
during_pandemic_strategies_bigram$percentage <- (during_pandemic_strategies_bigram$n / total_during_pandemic_bigram) * 100

# Comparing pre vs post covid for strategy unigrams (using percentage)
comparison_data_strategy <- full_join(pre_pandemic_strategies, during_pandemic_strategies, by = "word", suffix = c("_pre", "_during"))
comparison_data_strategy[is.na(comparison_data_strategy)] <- 0
comparison_data_strategy_long <- comparison_data_strategy %>% 
  gather(key = "period", value = "percentage", percentage_pre, percentage_during)

# Plot for strategy unigrams using percentage
ggplot(comparison_data_strategy_long, aes(x = reorder(word, percentage), y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Strategy Mentions Pre and During Pandemic (Percentage)", 
       x = "Strategies", y = "Percentage of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

# Comparing pre vs post covid for strategy bigrams (using percentage)
comparison_data_strategy_bigram <- full_join(pre_pandemic_strategies_bigram, during_pandemic_strategies_bigram, by = "word", suffix = c("_pre", "_during"))
comparison_data_strategy_bigram[is.na(comparison_data_strategy_bigram)] <- 0
comparison_data_strategy_bigram_long <- comparison_data_strategy_bigram %>% 
  gather(key = "period", value = "percentage", percentage_pre, percentage_during)

# Plot for strategy bigrams using percentage
ggplot(comparison_data_strategy_bigram_long, aes(x = reorder(word, percentage), y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Strategy Bigram Mentions Pre and During Pandemic (Percentage)", 
       x = "Strategy Bigrams", y = "Percentage of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

```

## Stategy Totals (Supports Nassens Findings - Self imposed disconnection strategies)

```{r echo=FALSE}
date_range_strat <- count_terms(date_range, strategy_unigrams)
date_range_strat_bigram <- count_terms(date_range, strategy_bigrams, "bigrams")

# Create the plot for unigrams
ggplot(date_range_strat, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[1]) +
  labs(title = "Strategy Totals for Unigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()


# Create the plot for bigrams
ggplot(date_range_strat_bigram, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[2]) +
  labs(title = "Strategy Totals for Bigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()

# Calculate total number of words for date_range period
total_words_date_range <- sum(date_range_strat$n)

# Calculate percentages for unigrams and bigrams
date_range_strat$percentage <- (date_range_strat$n / total_words_date_range) * 100
date_range_strat_bigram$percentage <- (date_range_strat_bigram$n / total_words_date_range) * 100

# Create the plot for unigrams with percentages
ggplot(date_range_strat, aes(x = reorder(word, percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[1]) +
  labs(title = "Strategy Totals for Unigrams (Percentage)", 
       x = "Platforms", y = "Percentage of Mentions") +
  theme_minimal() + coord_flip()

# Create the plot for bigrams with percentages
ggplot(date_range_strat_bigram, aes(x = reorder(word, percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[2]) +
  labs(title = "Strategy Totals for Bigrams (Percentage)", 
       x = "Platforms", y = "Percentage of Mentions") +
  theme_minimal() + coord_flip()



head(date_range_strat,10)
head(date_range_strat_bigram,10)
```
Alternative looks
```{r}
# Lollipop Chart for Unigrams
ggplot(date_range_strat, aes(x = reorder(word, n), y = n)) +
  geom_segment(aes(xend = reorder(word, n), yend = 0), color = brewer.pal(8, "Dark2")[1]) +
  geom_point(size = 3, color = brewer.pal(8, "Dark2")[1]) +
  labs(title = "Strategy Totals for Unigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()

# Lollipop Chart for Bigrams
ggplot(date_range_strat_bigram, aes(x = reorder(word, n), y = n)) +
  geom_segment(aes(xend = reorder(word, n), yend = 0), color = brewer.pal(8, "Dark2")[2]) +
  geom_point(size = 3, color = brewer.pal(8, "Dark2")[2]) +
  labs(title = "Strategy Totals for Bigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()

```


# Concerns/Opinions/Problems

```{r echo=FALSE}
# Define concerns
concern_unigrams <- c("anxiety", "stress", "addiction", "overwhelm", "overuse", "dependency", "distraction", "privacy", "isolation", "compulsion", "fatigue", "insecurity", "bias", "manipulation", "misinformation", "burnout", "exploitation", "alienation", "harassment", "bullying")
concern_bigrams <- c("information overload", "social isolation", "privacy breach", "mental fatigue", "digital addiction", "constant distraction", "data misuse", "platform bias", "screen burnout", "online harassment", "filter bubble", "echo chamber", "cyber bullying", "tech dependency", "cognitive decline", "data exploitation", "identity theft", "algorithmic bias", "invasive ads")

# Count occurrences for pre-pandemic and during pandemic for concern unigrams
pre_pandemic_concerns <- count_terms(pre_pandemic, concern_unigrams)
during_pandemic_concerns <- count_terms(during_pandemic, concern_unigrams)

# Count occurrences for pre-pandemic and during pandemic for concern bigrams
pre_pandemic_concerns_bigram <- count_terms(pre_pandemic, concern_bigrams, "bigrams")
during_pandemic_concerns_bigram <- count_terms(during_pandemic, concern_bigrams, "bigrams")

# Display top concern mentions for each period
head(pre_pandemic_concerns, 20)
head(during_pandemic_concerns, 20)
head(pre_pandemic_concerns_bigram, 20)
head(during_pandemic_concerns_bigram, 20)

# Comparing pre vs post covid for concern unigrams
comparison_data_concern <- full_join(pre_pandemic_concerns, during_pandemic_concerns, by = "word", suffix = c("_pre", "_during"))
comparison_data_concern[is.na(comparison_data_concern)] <- 0
comparison_data_concern_long <- comparison_data_concern %>% 
  gather(key = "period", value = "count", n_pre, n_during)

# Plot for concern unigrams
ggplot(comparison_data_concern_long, aes(x = reorder(word, count), y = count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Concern Mentions Pre and During Pandemic", 
       x = "Concerns", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

# Comparing pre vs post covid for concern bigrams
comparison_data_concern_bigram <- full_join(pre_pandemic_concerns_bigram, during_pandemic_concerns_bigram, by = "word", suffix = c("_pre", "_during"))
comparison_data_concern_bigram[is.na(comparison_data_concern_bigram)] <- 0
comparison_data_concern_bigram_long <- comparison_data_concern_bigram %>% 
  gather(key = "period", value = "count", n_pre, n_during)

# Plot for concern bigrams
ggplot(comparison_data_concern_bigram_long, aes(x = reorder(word, count), y = count, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Concern Bigram Mentions Pre and During Pandemic", 
       x = "Concern Bigrams", y = "Number of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip() + coord_flip()

```
As percentages
```{r}
# Calculate total mentions for each period for unigrams
total_pre_pandemic_concerns <- sum(comparison_data_concern$n_pre)
total_during_pandemic_concerns <- sum(comparison_data_concern$n_during)

# Calculate percentages for unigrams
comparison_data_concern$percentage_pre <- (comparison_data_concern$n_pre / total_pre_pandemic_concerns) * 100
comparison_data_concern$percentage_during <- (comparison_data_concern$n_during / total_during_pandemic_concerns) * 100

# Melt the data for ggplot for unigrams
comparison_data_concern_long_percentage <- comparison_data_concern %>% 
  gather(key = "period", value = "percentage", percentage_pre, percentage_during)

# Create the plot for unigrams using percentages
covid_concerns_uni_percentage <- ggplot(comparison_data_concern_long_percentage, aes(x = reorder(word, percentage), y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Concern Mentions Pre and During Pandemic (Percentage)", 
       x = "Concerns", y = "Percentage of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

# Calculate total mentions for bigrams for each period
total_pre_pandemic_concerns_bigram <- sum(comparison_data_concern_bigram$n_pre)
total_during_pandemic_concerns_bigram <- sum(comparison_data_concern_bigram$n_during)

# Calculate percentages for bigrams
comparison_data_concern_bigram$percentage_pre <- (comparison_data_concern_bigram$n_pre / total_pre_pandemic_concerns_bigram) * 100
comparison_data_concern_bigram$percentage_during <- (comparison_data_concern_bigram$n_during / total_during_pandemic_concerns_bigram) * 100

# Melt the data for ggplot for bigrams
comparison_data_concern_bigram_long_percentage <- comparison_data_concern_bigram %>% 
  gather(key = "period", value = "percentage", percentage_pre, percentage_during)

# Create the plot for bigrams using percentages
covid_concerns_bi_percentage <- ggplot(comparison_data_concern_bigram_long_percentage, aes(x = reorder(word, percentage), y = percentage, fill = period)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Comparison of Concern Bigram Mentions Pre and During Pandemic (Percentage)", 
       x = "Concern Bigrams", y = "Percentage of Mentions") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") + coord_flip()

covid_concerns_uni_percentage
covid_concerns_bi_percentage

```


## Concerns/Opinions/Problems

```{r echo=FALSE}
date_range_concerns <- count_terms(date_range, concern_unigrams)
date_range_concerns_bigram <- count_terms(date_range, concern_bigrams, "bigrams")

# Create the plot for unigrams
ggplot(date_range_concerns, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[1]) +
  labs(title = "Concerns Totals for Unigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()


# Create the plot for bigrams
ggplot(date_range_concerns_bigram, aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity", fill = brewer.pal(8, "Dark2")[2]) +
  labs(title = "Concerns Totals for Bigrams", 
       x = "Platforms", y = "Number of Mentions") +
  theme_minimal() + coord_flip()

head(date_range_concerns, 10)
head(date_range_concerns_bigram, 10)
```




















## Code summary

data_combined: This dataframe contains the combined posts and comments data.
date_range: Contains data filtered between January 1, 2019, and December 31, 2021.
pre_pandemic: Data filtered from January 1, 2019, to March 31, 2020 (pre-pandemic).
during_pandemic: Data filtered from April 1, 2020, to December 31, 2021 (during the pandemic).
pre_pandemic_platforms: Counts of platform unigram mentions during the pre-pandemic period.
during_pandemic_platforms: Counts of platform unigram mentions during the pandemic.
pre_pandemic_platforms_bigram: Counts of platform bigram mentions during the pre-pandemic period.
during_pandemic_platforms_bigram: Counts of platform bigram mentions during the pandemic.
date_range_platforms: Counts of platform unigram mentions in the date range (from 2019-01-01 to 2021-12-31).
date_range_platforms_bigram: Counts of platform bigram mentions in the date range (from 2019-01-01 to 2021-12-31).


```{r}
# List of dataframes to be printed
dataframes_list <- list(
  data_combined = data_combined,
  date_range = date_range,
  pre_pandemic = pre_pandemic,
  during_pandemic = during_pandemic,
  pre_pandemic_platforms = pre_pandemic_platforms,
  during_pandemic_platforms = during_pandemic_platforms,
  pre_pandemic_platforms_bigram = pre_pandemic_platforms_bigram,
  during_pandemic_platforms_bigram = during_pandemic_platforms_bigram,
  date_range_platforms = date_range_platforms,
  date_range_platforms_bigram = date_range_platforms_bigram
)

# Loop through the list and print the top 10 rows of each dataframe
for(df_name in names(dataframes_list)) {
  cat(paste("Head of", df_name, ":\n"))
  print(head(dataframes_list[[df_name]], 10))
  cat("\n")  # Add a newline for better formatting
}

```

